---
title: "Executing Reward with targets.R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{targets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction
This vignette discusses executing the RewardExecutionPackage with targets worklow framework.

# Installation
The first thing we're going to need is to create an renv for isolated reward execution.

```{r eval=FALSE}
install.packages("renv")
renv::init()
```
Next we will install the RewardExecutionPackage via github using remotes.

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("OHDSI/RewardExecutionPackage")
```
We now need to create our targets file that can be customized to our needs.

```{r eval=FALSE}
RewardExecuctionPackage::createTargetsFile()
```
This will create a file called `_targets.R` that will run the workflow.

We now need to create our yml configuration files for our CDMs.
These files store the information used to execute the package on Reward.

```{r eval = FALSE}
dir.create("cdmConfig")
RewardExecutionPackage::createCdmConfiguration("cdmConfig/myCdm.yml")
```
Edit this file with the settings for your CDM - take special note of the database connection fields, the password field
and the work schemas where docs will live.
You will be asked to enter and save a password for use with the database if you choose to have a password secured using
the keyring package.

For multiple cdms, just add the files to the cdmConfig directory.


# Get exported Reward references
We will need a set of references from the central reward database.
These will contain the cohorts that are to be executed.

# Execution
You can now execute the workflow with

```{r, eval=FALSE}
targets::tar_make()
```
This will take a long time to execute. If the execution pauses you can visualise the network to see what steps have been executed.

```{r, eval = FALSE}
targets::tar_visnetwork()
```

When the process completes, each CDM will have a zip folder containing all results that can be added to the central Reward server by the administrator.
# Optional - multiprocess execution
If you would like to run the execution in multiprocess mode (recommended) install the clustermq package.
Note that this may have additional setup requirements on your system.
Consult the [documentation](https://mschubert.github.io/clustermq/articles/userguide.html).
```{r, eval = FALSE}
install.packages('clustermq')
```

The execution can now run with:

```{r eval = FALSE}
targets::tar_make_clustermq(workers = 2)
```
Set the workers count to the number of simultaneous R processes you would like to run.
For more advanced cluster configuration see the [targets documentation](https://books.ropensci.org/targets/hpc.html).